FLM for growth as function of SPEI

### 2021-02-08 analysis/paper/vital rate models.Rmd
change to use `gratia` package to draw smooths instead of using cb_margeff() to draw marginal effects plots.

```{r}
draw(s_post_cf)
```

@@

```{r}
draw(s_post_1ha)
```

@@

Effect of size with all else held average.

```{r}
sr <- range(demog_post_cf$log_size_prev)

newdata_covar_cf <- 
  tibble(log_size_prev = seq(sr[1], sr[2], length.out = 100),
         plot = "newplot",
         year_fac = "newyear", 
         spei_history = mean(demog_post_cf$spei_history),
         L = demog_post_cf$L[1:100, ])
```

```{r}
out <- augment(s_post_cf, newdata = newdata_covar_cf, se_fit = TRUE)

covar_s_cf <-
  ggplot(out, aes(x = exp(log_size_prev), y = plogis(.fitted))) + 
  stat_summary_bin(geom = "point", fun = mean, aes(y = surv), data = demog_post_cf) +
  geom_ribbon(aes(ymin = plogis(.fitted - .se.fit * 1.96), ymax = plogis(.fitted + .se.fit * 1.96)), alpha = 0.3) +
  geom_line(color = "blue") +
  labs(x = TeX("size_t_"), y = "P(survival)") +
  theme_linedraw()

covar_s_cf
ggsave(here("analysis", "figures", "surv_cf_size.png"), covar_s_cf)
```
```{r}
demog_post_cf %>% filter(size_prev > 1500, surv == 0)

demog %>% filter(ha_id_number == 5310) %>% View()
```

```{r}
sr <- range(demog_post_1ha$log_size_prev)
newdata_covar_1ha <- 
  tibble(log_size_prev = seq(sr[1], sr[2], length.out = 100),
         plot = "newplot",
         year_fac = "newyear",
         spei_history = mean(demog_post_1ha$spei_history),
         L = demog_post_cf$L[1:100, ])

out <- augment(s_post_1ha, newdata = newdata_covar_1ha, se_fit = TRUE)

covar_s_1ha <-
  ggplot(out, aes(x = exp(log_size_prev), y = plogis(.fitted))) + 
  stat_summary_bin(geom = "point", fun = mean, aes(y = surv), data = demog_post_1ha) +
  geom_ribbon(aes(ymin = plogis(.fitted - .se.fit * 1.96), ymax = plogis(.fitted + .se.fit * 1.96)), alpha = 0.3) +
  geom_line(color = "blue") +
  labs(x = TeX("size_t_"), y = "P(survival)") +
  theme_linedraw()

covar_s_1ha
ggsave(here("analysis", "figures", "surv_1ha_size.png"), covar_s_1ha)
```

## Get plot data

```{r}
# use mean size plant across both habitats so plots are comparable
ref_data <-
  demog_post %>%
  dplyr::summarize(log_size_prev = log(mean(size_prev, na.rm = TRUE)),  #log of mean size, not mean of log_size
                   year_fac = "newyear",
                   plot = "newlevel")

```{r}
pred_s_post_cf  <- cb_margeff(s_post_cf,  Q = spei_history, L = L, ref_data = ref_data, cluster = cl)
pred_s_post_1ha <- cb_margeff(s_post_1ha, Q = spei_history, L = L, ref_data = ref_data, cluster = cl)
```

```{r}
surv_lim <- c(min(pred_s_post_1ha$fitted, pred_s_post_cf$fitted),
              max(pred_s_post_1ha$fitted, pred_s_post_cf$fitted))
# plogis(surv_lim)
```

## Plots

```{r}
p_surv_cf <-
  pred_s_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) + 
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  scale_fill_viridis_c("P(survival)", option = "A", limits = plogis(surv_lim)) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_surv_cf
ggsave(here("analysis", "figures", "surv_cf_spei.png"), p_surv_cf)
```

```{r}
p_surv_1ha <-
  pred_s_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  scale_fill_viridis_c("P(survival)", option = "A", limits = plogis(surv_lim)) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_surv_1ha
ggsave(here("analysis", "figures", "surv_1ha_spei.png"), p_surv_1ha)
```

**Slice through time at severe drought**

```{r}
p_surv_cf_slice <-
  pred_s_post_cf %>% 
  filter(nearest(x, -1.50)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:36) +
  labs(title = "Continuous Forest", y = "P(survival)") +
  theme_linedraw()
p_surv_cf_slice
```

```{r}
p_surv_1ha_slice <-
  pred_s_post_1ha %>% 
  filter(nearest(x, -1.5)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:36) +
  labs(title = "1-ha Fragments", y = "P(survival)") +
  theme_linedraw()
p_surv_1ha_slice
```

@@

```{r}
draw(g_post_cf)
```

@@

```{r}
# draw(g_post_1ha)
draw(g_post_1ha, select = 3, continuous_fill = scale_fill_viridis_c(option = "inferno"), contour = FALSE, fun = "exp")
ggsave("function_smooth-cb.png")
```

@@

Effect of size with all else held average.

```{r}
out <- augment(g_post_cf, newdata = newdata_covar_cf, se_fit = TRUE)

covar_growth_cf <-
  ggplot(out, aes(x = exp(log_size_prev), y = exp(.fitted))) + 
  geom_point(data = demog_post_cf, aes(x = size_prev, y = size), alpha = 0.1) +
  geom_ribbon(aes(ymin = exp(.fitted - .se.fit * 1.96), ymax = exp(.fitted + .se.fit * 1.96)), alpha = 0.3) +
  geom_abline(slope = 1, linetype = 2, color = "red") +
  geom_line(color = "blue") +
  # geom_rug(data = demog_post_cf, aes(x = size, y = size_next), alpha = 0.25) +
  theme_linedraw() +
  labs(x = TeX("size_t_"), y = TeX("size_{t+1}_"))
covar_growth_cf
ggsave(here("analysis", "figures", "growth_cf_size.png"), covar_growth_cf)
```
```{r}
out %>%
  filter(exp(log_size_prev) > exp(.fitted)) %>% # shinking plants
  pull(log_size_prev) %>% min() %>% exp() #first size at which shrinking happens.
```

```{r}
out <- augment(g_post_1ha, newdata = newdata_covar_1ha, se_fit = TRUE)

covar_growth_1ha <-
  ggplot(out, aes(x = exp(log_size_prev), y = exp(.fitted))) + 
  geom_point(data = demog_post_1ha, aes(x = size_prev, y = size), alpha = 0.1) +
  geom_ribbon(aes(ymin = exp(.fitted - .se.fit * 1.96), ymax = exp(.fitted + .se.fit * 1.96)), alpha = 0.3) +
  geom_abline(slope = 1, linetype = 2, color = "red") +
  geom_line(color = "blue") +
  # geom_rug(data = demog_post_1ha, aes(x = size, y = size_next), alpha = 0.25) +
  theme_linedraw() +
  labs(x = TeX("size_t_"), y = TeX("size_{t+1}_"))

covar_growth_1ha
ggsave(here("analysis", "figures", "growth_1ha_size.png"), covar_growth_1ha)
```
```{r}
out %>%
  filter(exp(log_size_prev) > exp(.fitted)) %>% #shrinking plants
  pull(log_size_prev) %>% min() %>% exp() #smallest size where plants start shrinking
```

## Get plot data

```{r}
pred_g_post_cf  <- cb_margeff(g_post_cf, Q = spei_history, L = L, ref_data = ref_data, cluster = cl)
pred_g_post_1ha <- cb_margeff(g_post_1ha, Q = spei_history, L = L, ref_data = ref_data, cluster = cl)
```

```{r}
mean_size # size in year t for fitted values

```{r}
shoot_lim <- c(min(pred_g_post_1ha$d_fitted, pred_g_post_cf$d_fitted),
               max(pred_g_post_1ha$d_fitted, pred_g_post_cf$d_fitted))
```

## Plots

```{r}
p_growth_cf <-
  pred_g_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = d_fitted, fill = d_fitted)) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  scale_fill_viridis_c(TeX("$\\Delta$ size"), option = "A", limits = shoot_lim) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_growth_cf
ggsave(here("analysis", "figures", "growth_cf_spei.png"), p_growth_cf)
```

```{r}
p_growth_1ha <-
  pred_g_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = d_fitted, fill = d_fitted)) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  scale_fill_viridis_c(TeX("$\\Delta$ size"), option = "A", limits = shoot_lim) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_growth_1ha
ggsave(here("analysis", "figures", "growth_1ha_spei.png"), p_growth_1ha)
```

**Slice through time at severe drought**

```{r}
# p_growth_cf_slice <-
#   pred_g_post_cf %>% 
#   filter(nearest(x, -1.50)) %>% 
#   ggplot(aes(x = lag, y = exp(fitted))) +
#   geom_ribbon(aes(
#     ymin = exp(fitted - se.fit * 1.96),
#     ymax = exp(fitted + se.fit * 1.96)
#   ), alpha = 0.3)+
#   geom_line() +
#   scale_x_continuous("lag(months)", breaks = 0:36) +
#   labs(title = "Continuous Forest", y = "shoots (t+1)") +
#   theme_linedraw()
# p_growth_cf_slice
```

```{r}
# p_growth_1ha_slice <-
#   pred_g_post_1ha %>% 
#   filter(nearest(x, -1.5)) %>% 
#   ggplot(aes(x = lag, y = exp(fitted))) +
#   geom_ribbon(aes(
#     ymin = exp(fitted - se.fit * 1.96),
#     ymax = exp(fitted + se.fit * 1.96)
#   ), alpha = 0.3)+
#   geom_line() +
#   scale_x_continuous("lag(months)", breaks = 0:36) +
#   labs(title = "1-ha Fragments", y = "shoots (t+1)") +
#   theme_linedraw()
# p_growth_1ha_slice
```

**Slice through individual months**
TODO: Change to ridge plots?

I find this less useful, but just shows that relationships are slightly quadratic at most complicated.  This would be more useful if there was a way to show which lines had "slopes" significantly different from 0 (i.e. don't totally overlap a flat line).

```{r}
# #TODO: replace with ridge plot
# plotdf <-
#   pred_g_post_cf %>% 
#   mutate(lag = round(lag)) %>% 
#   group_by(x, lag) %>% 
#   summarize(across(everything(),  mean))
# 
# foo <- function(x) {
#   x <- as.numeric(x)
#   mon <- month(ymd("2020-2-01") - months(x), label = TRUE)
#   l <- glue("lag={x} ({mon})")
#   return(l)
# }
# 
# p_growth_cf_months <-
#   plotdf %>% 
#   ggplot(aes(x = x, y = exp(fitted))) +
#   geom_ribbon(aes(
#     ymin = exp(fitted - se.fit * 1.96),
#     ymax = exp(fitted + se.fit * 1.96)
#   ), alpha = 0.3)+
#   geom_line() +
#   scale_x_continuous("SPEI3") +
#   scale_y_continuous("shoots (t+1)") +
#   facet_wrap(~lag, labeller = as_labeller(foo)) +
#   theme_bw()
# p_growth_cf_months
```

@@

```{r}
draw(f_post_cf)
```

@@

```{r}
draw(f_post_1ha)
```

@@

Effect of size with all else held average.

```{r}
out <- augment(f_post_cf, newdata = newdata_covar_cf, se_fit = TRUE)

covar_f_cf <-
  ggplot(out, aes(x = exp(log_size_prev), y = plogis(.fitted))) + 
  stat_summary_bin(geom = "point", fun = mean, aes(y = flwr), data = demog_post_cf) +
  geom_ribbon(aes(ymin = plogis(.fitted - .se.fit * 1.96), ymax = plogis(.fitted + .se.fit * 1.96)), alpha = 0.3) +
  geom_line(color = "blue") +
  labs(x = TeX("size_t_"), y = "P(flowering)") +
  theme_linedraw()

covar_f_cf
ggsave(here("analysis", "figures", "flwr_cf_size.png"), covar_f_cf)
```

```{r}
out <- augment(f_post_1ha, newdata = newdata_covar_1ha, se_fit = TRUE)

covar_f_1ha <-
  ggplot(out, aes(x = exp(log_size_prev), y = plogis(.fitted))) + 
  stat_summary_bin(geom = "point", fun = mean, aes(y = flwr), data = demog_post_1ha) +
  geom_ribbon(aes(ymin = plogis(.fitted - .se.fit * 1.96), ymax = plogis(.fitted + .se.fit * 1.96)), alpha = 0.3) +
  geom_line(color = "blue") +
  labs(x = TeX("size_t_"), y = "P(flowering)") +
  theme_linedraw()

covar_f_1ha
ggsave(here("analysis", "figures", "flwr_1ha_size.png"), covar_f_1ha)
```

## Get plot data

@@

```{r}
pred_f_post_cf  <- cb_margeff(f_post_cf,  Q = spei_history, L = L, ref_data = ref_data, cluster = cl)
pred_f_post_1ha <- cb_margeff(f_post_1ha, Q = spei_history, L = L, ref_data = ref_data, cluster = cl)
```

@@

```{r}
flowered_lim <- c(min(pred_f_post_1ha$fitted, pred_f_post_cf$fitted),
                  max(pred_f_post_1ha$fitted, pred_f_post_cf$fitted))
plogis(flowered_lim)
```

## Plots

```{r}
p_flowered_cf <-
  pred_f_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) + 
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  scale_fill_viridis_c("P(flowering)", option = "A", limits = plogis(flowered_lim)) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_flowered_cf
ggsave(here("analysis", "figures", "flwr_cf_spei.png"), p_flowered_cf)
```

```{r}
p_flowered_1ha <-
  pred_f_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) + 
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  scale_fill_viridis_c("P(flowering)", option = "A", limits = plogis(flowered_lim)) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_flowered_1ha
ggsave(here("analysis", "figures", "flwr_1ha_spei.png"), p_flowered_1ha)
```
very similar to growth

**Slice through time at severe drought**

```{r}
p_flowered_cf_slice <-
  pred_f_post_cf %>% 
  filter(nearest(x, -1.50)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:36) +
  labs(title = "Continuous Forest", y = "P(flowering)") +
  theme_linedraw() 
p_flowered_cf_slice
```

```{r}
p_flowered_1ha_slice <-
  pred_f_post_1ha %>% 
  filter(nearest(x, -1.5)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:36) +
  labs(title = "1-ha Fragments", y = "P(flowering)") +
  theme_linedraw()
p_flowered_1ha_slice
```

# Plots
## Growth
```{r}
p_growth_spei <-
  (p_growth_cf | p_growth_1ha) +
  plot_annotation(title = "Effect of drought on growth") +
  plot_layout(guides = "collect") & theme_talk & labs(caption = "")
p_growth_spei
# ggsave(here("analysis", "figures", "growth_spei.png"), p_growth_spei, height = 7, width = 14)
```

@@

These aren't significant.

```{r}
p_surv_spei <- 
  (p_surv_cf|p_surv_1ha) + 
  plot_annotation(title = "Effect of drought on survival") +
  plot_layout(guides = "collect") & theme_talk & labs(caption="")
p_surv_spei
# ggsave(here("analysis", "figures", "surv_spei.png"), p_surv_spei, width = 14, height = 7)
```

```{r}
p_flowered_spei <- 
  (p_flowered_cf|p_flowered_1ha) + 
  plot_annotation(title = "Effect of drought on flowering") +
  plot_layout(guides = "collect") & theme_talk & labs(caption = "")
p_flowered_spei
# ggsave(here("analysis", "figures", "flowering_spei.png"), p_flowered_spei, width = 14, height = 7)
```

>>>>

@@

@@

Plot smooth for size

```{r}
s_1ha_eval1 <-
  smooth_estimates(s_post_1ha, smooth = "log_size_prev", unconditional = TRUE) %>% 
  add_confint() %>% 
  mutate(across(c(est, lower_ci, upper_ci), ~plogis(.x + coef(s_post_1ha)[1])))

ggplot(s_1ha_eval1, aes(x = log_size_prev)) +
  geom_line(aes(y = est)) +
  geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci), alpha = 0.25) +
  geom_rug(data = model.frame(s_post_1ha)) +
  theme_bw() +
  labs(x = TeX("$log(size_t)$"), y = "P(survival)", title = "1-ha fragments")
ggsave(here("analysis", "figures", "surv_1ha_size.png"))
```

```{r}
s_cf_eval1 <-
  smooth_estimates(s_post_cf, smooth = "log_size_prev", unconditional = TRUE) %>% 
  add_confint() %>% 
  mutate(across(c(est, lower_ci, upper_ci), ~plogis(.x + coef(s_post_cf)[1])))

ggplot(s_cf_eval1, aes(x = log_size_prev)) +
  geom_line(aes(y = est)) +
  geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci), alpha = 0.25) +
  geom_rug(data = model.frame(s_post_cf)) + 
  theme_bw() +
  labs(x = TeX("$log(size_t)$"), y = "P(survival)", title = "Continuous forest")
ggsave(here("analysis", "figures", "surv_cf_size.png"))
```

## Crossbasis plot

`dist` isn't working yet in `smooth_estimates`, but that's ok because I don't need CI for these plots (yet).

```{r}
s_1ha_eval <-
  evaluate_smooth(s_post_1ha, smooth = "spei_history", dist = 0.1) %>% 
  mutate(est = plogis(est + coef(s_post_1ha)[1]))
s_cf_eval <-
  evaluate_smooth(s_post_cf, smooth = "spei_history", dist = 0.1) %>% 
  mutate(est = plogis(est + coef(s_post_cf)[1]))

surv_lims <- c(min(s_1ha_eval$est, s_cf_eval$est, na.rm = TRUE),
                  max(s_1ha_eval$est, s_cf_eval$est, na.rm = TRUE))
```

```{r}
ggplot(s_1ha_eval, aes(x = spei_history, y = L, fill = est, z = est)) +
  geom_raster() +
  geom_contour(color = "black", binwidth = 0.002) +
  scale_fill_viridis_c("P(survival)", option = "magma", limits = surv_lims) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  labs(title = "1ha fragments") +
  theme_bw()
ggsave(here("analysis", "figures", "surv_1ha_spei.png"))
```
```{r}
ggplot(s_cf_eval, aes(x = spei_history, y = L, fill = est, z = est)) +
  geom_raster() +
  geom_contour(color = "black", binwidth = 0.002) +
  scale_fill_viridis_c("P(survival)", option = "magma", limits = surv_lims) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) + 
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  labs(title = "Continuous forest") +
  theme_bw()
ggsave(here("analysis", "figures", "surv_cf_spei.png"))
```

@@

@@

@@

```{r}
g_1ha_eval1 <-
  smooth_estimates(g_post_1ha, smooth = "log_size_prev", unconditional = TRUE) %>% 
  add_confint() %>% 
  mutate(across(c(est, lower_ci, upper_ci), ~.x + coef(s_post_1ha)[1]))

ggplot(g_1ha_eval1, aes(x = log_size_prev)) +
  geom_line(aes(y = est)) +
  # geom_abline(slope = 1, linetype = 2, color = "red") +
  geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci), alpha = 0.25) +
  geom_rug(data = model.frame(g_post_1ha)) +
  theme_bw() +
  labs(x = TeX("$log(size_t)$"), y = TeX("$log(size_{t+1})"), title = "1-ha fragments")
ggsave(here("analysis", "figures", "growth_1ha_size.png"))
```
```{r}
g_cf_eval1 <-
  smooth_estimates(g_post_cf, smooth = "log_size_prev", unconditional = TRUE) %>% 
  add_confint() %>% 
  mutate(across(c(est, lower_ci, upper_ci), ~.x + coef(s_post_cf)[1]))

ggplot(g_cf_eval1, aes(x = log_size_prev)) +
  geom_line(aes(y = est)) +
  # geom_abline(slope = 1, linetype = 2, color = "red") +
  geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci), alpha = 0.25) +
  geom_rug(data = model.frame(g_post_cf)) +
  theme_bw() +
  labs(x = TeX("$log(size_t)$"), y = TeX("$log(size_{t+1})"), title = "Continuous forest")
ggsave(here("analysis", "figures", "growth_cf_size.png"))
```

## Crossbasis plot
`dist` isn't working yet in `smooth_estimates`, but that's ok because I don't need CI for these plots (yet).

```{r}
g_1ha_eval <-
  evaluate_smooth(g_post_1ha, smooth = "spei_history", dist = 0.1) #%>% 
  # mutate(est = est + coef(g_post_1ha)[1])
g_cf_eval <-
  evaluate_smooth(g_post_cf, smooth = "spei_history", dist = 0.1) # %>% 
  # mutate(est = est + coef(g_post_cf)[1])

grow_lims <- c(min(g_1ha_eval$est, g_cf_eval$est, na.rm = TRUE),
               max(g_1ha_eval$est, g_cf_eval$est, na.rm = TRUE))
```

```{r}
ggplot(g_1ha_eval, aes(x = spei_history, y = L, fill = est, z = est)) +
  geom_raster() +
  geom_contour(color = "black", binwidth = 0.1) +
  scale_fill_viridis_c("∆Size (?)", option = "magma", limits = grow_lims) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  labs(title = "1ha fragments") +
  theme_bw()
ggsave(here("analysis", "figures", "growth_1ha_spei.png"))
```
```{r}
ggplot(g_cf_eval, aes(x = spei_history, y = L, fill = est, z = est)) +
  geom_raster() +
  geom_contour(color = "black", binwidth = 0.1) +
  scale_fill_viridis_c("∆Size (?)", option = "magma", limits = grow_lims) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  labs(title = "Continuous forest") +
  theme_bw()
ggsave(here("analysis", "figures", "growth_cf_spei.png"))
```

@@

@@

@@

Plot smooth for size

```{r}
f_1ha_eval1 <-
  smooth_estimates(f_post_1ha, smooth = "log_size_prev", unconditional = TRUE) %>% 
  add_confint() %>% 
  mutate(across(c(est, lower_ci, upper_ci), ~plogis(.x + coef(f_post_1ha)[1])))

ggplot(f_1ha_eval1, aes(x = log_size_prev)) +
  geom_line(aes(y = est)) +
  geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci), alpha = 0.25) +
  # stat_summary_bin(geom = "point", fun = mean, aes(y = flwr), data = model.frame(f_post_1ha)) +
  geom_rug(data = model.frame(f_post_1ha)) +
  theme_bw() +
  labs(x = TeX("$log(size_t)$"), y = "P(flowering)", title = "1-ha fragments")
ggsave(here("analysis", "figures", "flwr_1ha_size.png"))
```

```{r}
f_cf_eval1 <-
  smooth_estimates(f_post_cf, smooth = "log_size_prev", unconditional = TRUE) %>% 
  add_confint() %>% 
  mutate(across(c(est, lower_ci, upper_ci), ~plogis(.x + coef(f_post_cf)[1])))

ggplot(f_cf_eval1, aes(x = log_size_prev)) +
  geom_line(aes(y = est)) +
  geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci), alpha = 0.25) +
  # stat_summary_bin(geom = "point", fun = mean, aes(y = flwr), data = model.frame(f_post_cf)) +
  geom_rug(data = model.frame(f_post_cf)) +
  theme_bw() +
  labs(x = TeX("$log(size_t)$"), y = "P(flowering)", title = "Continuous forest")
ggsave(here("analysis", "figures", "flwr_cf_size.png"))
```

## Crossbasis plot

`dist` isn't working yet in `smooth_estimates`, but that's ok because I don't need CI for these plots (yet).

```{r}
f_1ha_eval <-
  evaluate_smooth(f_post_1ha, smooth = "spei_history", dist = 0.1) %>% 
  mutate(est = plogis(est + coef(f_post_1ha)[1]))
f_cf_eval <-
  evaluate_smooth(f_post_cf, smooth = "spei_history", dist = 0.1) %>% 
  mutate(est = plogis(est + coef(f_post_cf)[1]))

flwr_lims <- c(min(f_1ha_eval$est, f_cf_eval$est, na.rm = TRUE),
               max(f_1ha_eval$est, f_cf_eval$est, na.rm = TRUE))
```

```{r}
ggplot(f_1ha_eval, aes(x = spei_history, y = L, fill = est, z = est)) +
  geom_raster() +
  geom_contour(color = "black", binwidth = 0.001) +
  scale_fill_viridis_c("P(flowering)", option = "magma", limits = flwr_lims) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  labs(title = "1ha fragments") +
  theme_bw()
ggsave(here("analysis", "figures", "flwr_1ha_spei.png"))
```
```{r}
ggplot(f_cf_eval, aes(x = spei_history, y = L, fill = est, z = est)) +
  geom_raster() +
  geom_contour(color = "black", binwidth = 0.001) +
  scale_fill_viridis_c("P(flowering)", option = "magma", limits = flwr_lims) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) + 
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  labs(title = "Continuous forest") +
  theme_bw()
ggsave(here("analysis", "figures", "flwr_cf_spei.png"))
```

# Plots
## Growth

### Get plot data

@@

```{r eval=FALSE}
pred_g_post_cf  <- cb_margeff(g_post_cf, Q = spei_history, L = L, ref_data = ref_data, cluster = cl)
pred_g_post_1ha <- cb_margeff(g_post_1ha, Q = spei_history, L = L, ref_data = ref_data, cluster = cl)
```

```{r eval=FALSE}
mean_size # size in year t for fitted values

@@

```{r eval=FALSE}
shoot_lim <- c(min(pred_g_post_1ha$d_fitted, pred_g_post_cf$d_fitted),
               max(pred_g_post_1ha$d_fitted, pred_g_post_cf$d_fitted))
```

### Plots

```{r eval=FALSE}
p_growth_cf <-
  pred_g_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = d_fitted, fill = d_fitted)) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  scale_fill_viridis_c(TeX("$\\Delta$ size"), option = "A", limits = shoot_lim) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_growth_cf
ggsave(here("analysis", "figures", "growth_cf_spei.png"), p_growth_cf)
```

```{r eval=FALSE}
p_growth_1ha <-
  pred_g_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = d_fitted, fill = d_fitted)) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  scale_fill_viridis_c(TeX("$\\Delta$ size"), option = "A", limits = shoot_lim) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_growth_1ha
ggsave(here("analysis", "figures", "growth_1ha_spei.png"), p_growth_1ha)
```

@@

### Get plot data

```{r eval=FALSE}
# use mean size plant across both habitats so plots are comparable
ref_data <-
  demog_post %>%
  dplyr::summarize(log_size_prev = log(mean(size_prev, na.rm = TRUE)),  #log of mean size, not mean of log_size
                   year_fac = "newyear",
                   plot = "newlevel")

```{r eval=FALSE}
pred_s_post_cf  <- cb_margeff(s_post_cf,  Q = spei_history, L = L, ref_data = ref_data, cluster = cl)
pred_s_post_1ha <- cb_margeff(s_post_1ha, Q = spei_history, L = L, ref_data = ref_data, cluster = cl)
```

```{r eval=FALSE}
surv_lim <- c(min(pred_s_post_1ha$fitted, pred_s_post_cf$fitted),
              max(pred_s_post_1ha$fitted, pred_s_post_cf$fitted))
# plogis(surv_lim)
```

### Plots

```{r eval=FALSE}
p_surv_cf <-
  pred_s_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) + 
  scale_x_continuous(TeX("SPEI_3_"), expand = c(0,0)) +
  scale_fill_viridis_c("P(survival)", option = "A", limits = plogis(surv_lim)) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_surv_cf
ggsave(here("analysis", "figures", "surv_cf_spei.png"), p_surv_cf)
```
